GPU-based Adaptive Beamforming for Active Sonar Imaging

### 2012-05-07 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:07	21:12:22	(Mon 7.May)

In a typical active sonar imaging scenario encoded signals are transmitted towards a surface of interest, and the resulting reflections are recorded using an array of receivers. These receivers may be independently delayed and weighted to adjust the array's point of focus, a concept commonly referred to as beamforming.

@@

The receiver outputs can then be coherently combined in the post-processing to focus on specific points in the image. The combination process involves assigning suitable delays and weights to the array's channels, and is commonly referred to as beamforming.

In a typical active sonar imaging scenario encoded signals are transmitted towards a surface interest, and the resulting reflections are recorded using an array of receivers. This is favourable setup as it allows the receiver outputs to be coherently combined in the post-processing to focus on specific points in the image. The combination process involves assigning suitable delays and weights to the array's channels, and is commonly referred to as beamforming.

>>>>

In a typical active sonar imaging scenario encoded signals are transmitted towards a surface of interest, and the resulting reflections are recorded using an array of receivers. The receiver outputs are then coherently combined in the post-processing to focus on specific points in the image. This involves assigning suitable delays and weights to the array's channels, a concept commonly referred to as beamforming.

@@

The fundamental problem of sonar imaging is to estimate each pixel's individual contribution to the final recorded echo. If the data is digitally stored, we can perform this task by focusing on one pixel at a time in the post-processing. Since the geometric relationship of the array and image is known, one usually start by selecting delays that mitigates the difference in transmitter-pixel-receiver propagation time. the delays are usually simply chosen to .
